---
title: "FunEnrich"
author: "Gregorio Alanis-Lobato"
date: false
output: rmarkdown::github_document
---

BP, CC, MF (i.e. Gene Ontology) and REACTOME enrichment analyses for a list of 
genes of interest, given a list of background genes.

The package supports ENTREZIDs (default), GENE SYMBOLs and UNIPROT accessions.

# Installation

1. Install the `devtools` package from CRAN if you haven't done so:

```r
install.packages("devtools")
```

2. Load the `devtools` package:

```r
library("devtools")
```

3. Install `FunEnrich` using the `install_github` function:

```r
install_github("galanisl/FunEnrich")
```

# Usage

To start using `FunEnrich`, load the package:

```{r message=FALSE, warning=FALSE}
library("FunEnrich")
```

Let's now use the gene-disease associations included in the package. We will use
`disease.genes` as background and genes associated with `metabolic` disorders as
genes of interest (type `?metabolic` and `?disease.genes` in R for more 
information about these datasets):

```{r message=FALSE, warning=FALSE}
analysis <- fun_enrich(gene.list = metabolic, background = disease.genes, 
                       id.type = "ENTREZID", benjamini = FALSE)
```

We can now explore, for example, the Molecular Functions enriched in genes that 
are specifically associated with metabolic disorders...

```{r}
head(analysis$mf)
```

... as well as the enriched REACTOME pathways:

```{r}
head(analysis$reactome)
```

It is also possible to generate a bar plot that focuses on the most enriched
term of one or all categories:

```{r}
plot_fun_enrich(enr = analysis, aspect = "ALL", benjamini = F, 
                top = 5, char_per_line = 80)
```

